Single-cell virus sequencing of influenza infections that trigger innate immunity

### 2018-12-24 paper/paper.tex
re-worked abstract to emphasize stochasticity and indicate that most defects are not statistically significantly associated with IFN

\section*{SUMMARY}
{\bf
The outcome of viral infection is extremely heterogeneous, with infected cells only sometimes activating innate immunity.  
Here we assess how the genetic variation inherent in viral populations contributes to this heterogeneity.
We do this by developing a new approach to determine both the transcriptome and full-length sequences of all viral genes in single influenza-infected cells.
Infections that activate an innate-immune response in single cells are often initiated by virions with defects that include amino-acid mutations, internal deletions, and failure to express key genes.  
However, immune activation remains stochastic in cells infected by virions with these defects, and sometimes occurs even in cells infected by virions that express unmutated copies of all genes.
Our work shows that the genetic variation present in influenza virus populations contributes to but does not fully explain the heterogeneity in infection outcome and immune activation in single infected cells.
}

\vspace{0.2in}
\keywords{PacBio, influenza, interferon, single-cell RNA-seq, NS1, stochastic}

>>>>

\section*{SUMMARY}
{\bf
The outcome of viral infection is extremely heterogeneous, with infected cells only sometimes activating innate immunity.  
Here we develop a new approach to assess how the genetic variation inherent in viral populations contributes to this heterogeneity.
We do this by determining both the transcriptome and full-length sequences of all viral genes in single influenza-infected cells.
Most cells are infected by virions with defects such as amino-acid mutations, internal deletions, or failure to express a gene.
We identify instances of each type of defect that increase the likelihood that a cell activates an innate-immune response.
However, immune activation remains stochastic in cells infected by virions with these defects, and sometimes occurs even when a cell is infected by a virion that expresses unmutated copies of all genes.
Our work shows that viral genetic variation substantially contributes to but does not fully explain the heterogeneity in single influenza-infected cells.
}

\vspace{0.2in}
\keywords{PacBio, single-cell RNA-seq, influenza, interferon, NS1, stochastic}
